$K$-corrections and photometric redshifts in GALEX, SDSS, 2MASS, DEEP, and Spitzer data$^1$

### 2005-03-15 docs/paper/kcorrect.tex
some writing
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@344 75dff457-8751-0410-ab1a-cd701654ce6b

\title{$K$-corrections and photometric redshifts in SDSS and 2MASS$^1$}

@@

\begin{abstract}
We present a method to develop templates for calculating
$K$-corrections and photometric redshifts suitable for ultraviolet,
optical, and infrared observations. Since we base the templates on
stellar population synthesis results, the results are intepretable in
terms of approximate stellar masses and star-formation histories. We
present templates fit with this method to the Sloan Digital Sky Survey
and Two-Micron All Sky Survey photometry.  The software that generates
these results is publicly available and easily adapted to handle a
wide range of galaxy observations.
\end{abstract}

>>>>

\title{$K$-corrections and photometric redshifts in GALEX, SDSS,
2MASS, DEEP, and Spitzer data$^1$}

@@

\begin{abstract}
We present a method to develop templates for calculating
$K$-corrections and photometric redshifts suitable for ultraviolet,
optical, and infrared observations. Since we base the templates on
stellar population synthesis results, the results are intepretable in
terms of approximate stellar masses and star-formation histories. We
present templates fit with this method to data from GALEX, Sloan
Digital Sky Survey spectroscopy and photometry, the Two-Micron All Sky
Survey, the Deep Extragalactic Evolutionary Probe, and the Spitzer
Space Telescope. In addition, we provide software for using such data
to estimate $K$-corrections, photometric redshifts, evolution
corrections, stellar masses, star formation histories, and
spectroscopic continua suitable for use in emission line measurements.
This software is suitable for analyzing many other data sets.
\end{abstract}code
